---
title: "An example workflow of building energy model calibration"
author:
  - Hongyuan Jia
  - Adrian Chong
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: yes
        toc_float:
            collapsed: false
            smooth_scroll: false
        fig_caption: yes
        theme: yeti
---

```{r setup, include = FALSE}
library(tidyverse, warn.conflicts = FALSE) # data analysis
library(eplusr)                            # integration with EnergyPlus
library(here)                              # project-root-based file path

# disable verbose information
eplusr_option(verbose_info = FALSE)

# install EnergyPlus v9.1 used in this workflow if necessary
if (!is_avail_eplus(9.1)) install_eplus(9.1, local = TRUE)
```

# Workflow

<!-- Create a workflow diagram? -->

# Create synthetic meter data

* Read un-calibrated model
* Set calibration inputs and outputs
* Use AMY weather file to generate synthetic measured data
* Extract synthetic meter data and save it as a csv file

## Read original un-calibrated model

```{r read-ori}
idf <- read_idf(here("data-raw/idf/Singapore_Concrete_Benchmark_Model.idf"))

# remove all existing outputs
idf$`Output:Variable` <- NULL
idf$`Output:Meter:MeterFileOnly` <- NULL
```

## Calibration inputs, outputs and calibration parameters

Calibration parameters:

* LPD (Lighting Power Density) (`Watts per Zone Floor Area` field in `Lights` class)
* Conductivity of exterior walls (`Conductivity` in `Material` class) <!-- "MaterialProperties" in the paper figures -->

Input:

* AMY weather <!-- "Weather_AMY" in the paper figures -->

Outputs:

* Hourly(?) building total electricity energy (`Electricity:Building` meter) <!-- "Building_Electricity" in the paper figures -->

```{r add-outputs}
idf$add(Output_Meter = list("Electricity:Building", "Hourly"))
```

Update `RunPeriod` to match the AMY year

```{r runperiod}
# update RunPeriod to correctly indicate an AMY EPW file is used
idf$RunPeriod[[1]]$Name <- "Singapore 2018"
idf$RunPeriod[[1]]$`Begin Year` <- 2018

# day of week for start day will be automatically calculated based on begin year
idf$RunPeriod[[1]]$`Day of Week for Start Day` <- NULL

# save the model
idf$save(here("data/idf/AMY.idf"), overwrite = TRUE)
```

```{r run-amy}
# path of AMY EPW
path_amy <- here("data-raw/epw/AMY/SGP_SINGAPORE-CHANGI-AP_486980_18.epw")

# run annual simulation for AMY
idf$run(path_amy, here("data/sim/AMY"), echo = FALSE)
```

Extract hourly electricity

```{r elec}
job <- idf$last_job()
elec <- job$report_data(name = "Electricity:Building", environment_name = "Singapore 2018")

# convert to kWh
elec <- elec %>%
    mutate(
        value = units::set_units(value, "J") %>%
            units::set_units("kWh") %>%
            units::drop_units(),
        units = "kWh"
    )
```
