---
title: "An example workflow of building energy model calibration"
author:
  - Hongyuan Jia
  - Adrian Chong
date: "`r Sys.Date()`"
output:
    html_document:
        toc: yes
        toc_float:
            collapsed: false
            smooth_scroll: false
        fig_caption: yes
        theme:
            version: 4
            bootswath: flatly
---

```{r setup, include = FALSE}
library(tidyverse, warn.conflicts = FALSE) # data analysis
library(lubridate, warn.conflicts = FALSE) # work with date time
library(eplusr)                            # integration with EnergyPlus
library(here)                              # project-root-based file path

# disable verbose information
eplusr_option(verbose_info = FALSE)

# install EnergyPlus v9.1 used in this workflow if necessary
if (!is_avail_eplus(9.1)) install_eplus(9.1, local = TRUE)

# load helper functions
source(here("R/functions.R"))
```

# Workflow

<!-- Create a workflow diagram? -->

- The model we choose with brief description

# Create synthetic meter data

- Read the original baseline model
- Define observed inputs, outputs and calibration parameters
- Run simulation to create synthetic data

## Read original baseline model

Here, we use the reference large office building building for Singapore
developed by Duarte, Raftery and Schiavon.

First, we read the baseline model using the `eplusr::read_idf()` function.

```{r read-ori}
# path of the baseline model
path_base <- here("data-raw/idf/Singapore_Concrete_Benchmark_Model.idf")

# read baseline model
base <- read_idf(path_base)
```

We remove all outputs in the baseline model. So

```{r rem-outputs}
# remove all existing outputs
base$`Output:Variable` <- NULL
base$`Output:Meter:MeterFileOnly` <- NULL
```

## Observed inputs, outputs and calibration parameters

We choose AMY (Annual Meteorological Year) as the observed input.
AMY together with other separate local weather variables are commonly used as
the observed inputs for calibration.

For calibration parameters, we select 6 most commonly used ones for
demonstration, including:

- Material properties
- Infiltration rate
- Occupancy density
- Lighting power density
- Electric equipment power density
- Cooling setpoint

The mapping between those parameters and corresponding EnergyPlus inputs for
the baseline model are listed in the table blow:

| Calibration parameter            | Class                             | Object                                   | Field                                     | Value |
|----------------------------------+-----------------------------------+------------------------------------------+-------------------------------------------+-------|
| Material properties              | `Material`                        | `SGP_Concrete_200mm`                     | `Conductivity {W/m-K}`                    | 1.442 |
|                                  |                                   |                                          | `Density {kg/m3}`                         | 2400  |
|                                  |                                   |                                          | `Specific Heat {J/kg-K}`                  | 832   |
| Infiltration rate                | `ZoneInfiltration:DesignFlowRate` | All `*_Infiltration` objects for offices | `Air Changes per Hour {1/hr}`             | 0.2   |
| Occupancy density                | `People`                          | All objects for offices                  | `Zone Floor Area per Person {m2/persion}` | 10    |
| Lighting power density           | `Lights`                          | All `*_Lights` objects for offices       | `Watts per Zone Floor Area {W/m2}`        | 15    |
| Electric equipment power sensity | `ElectricEquipment`               | All `*_Equip` objects for offices        | `Watts per Zone Floor Area {W/m2}`        | 14    |
| Cooling setpoint                 | `Schedule:Compact`                | `Sch_Zone_Cooling_Setpoint_Wo_Solar`     | `Field 4`                                 | 24    |
|                                  |                                   | `Sch_Zone_Cooling_Setpoint_Solar`        | `Field 4`                                 | 23    |

For observed output, we choose hourly building electricity consumption. All
calibration parameters are commonly used together with building electricity
consumption in calibration studies we investigated. The corresponding output
variable in EnergyPlus is `Electriity: Building` with `Hourly` reporting
frequency.

Next, we run the baseline model using AMY EPW file to create synthetic observed
output using simulations. The data will present noise-free measurements which
functions as a surrogate for clean sensor data.

Below we made some necessary to the baseline model, including adding the output
meter and setting the begin year of `RunPeriod` objects based on our AMY
weather data. We saved the modifed model as `AMY.idf` in the `data/idf` folder.

```{r add-outputs}
# add hourly building electricity output meter
base$add(Output_Meter = list("Electricity:Building", "Hourly"))

# update RunPeriod to correctly indicate an AMY EPW file is used
base$RunPeriod[[1]]$Name <- "Singapore 2018"
base$RunPeriod[[1]]$`Begin Year` <- 2018

# day of week for start day will be automatically calculated based on begin year
base$RunPeriod[[1]]$`Day of Week for Start Day` <- NULL

# save the model
base$save(here("data/idf/base.idf"), overwrite = TRUE)
```

## Run simulation to create synthetic data

Below we ran an annual simulation using the AMY EPW stored in
`data-raw/epw/AMY` folder.

```{r run-base}
# path of AMY EPW
path_epw_amy <- here("data-raw/epw/AMY/SGP_SINGAPORE-CHANGI-AP_486980_18.epw")

# run annual simulation for AMY
base$run(path_epw_amy, here("data/sim/base"), echo = FALSE)
```

Once the simulation completed, we extracted the output using `$report_data()`
method, convert the unit of electricity from Joules to kWh and save the values
together with the timestamp to a csv file named `synthetic_meter.csv` in the
`data` folder.

```{r meter-base}
meter_base <- base %>% extract_electricity()

# save synthetic meter data
write_csv(meter_base, here("data/synthetic_meter.csv"))
```

# Session Info

```{r session-info}
sessionInfo()
```
