---
title: "An example workflow of building energy model calibration"
author:
  - Hongyuan Jia
  - Adrian Chong
date: "`r Sys.Date()`"
output:
    html_document:
        toc: yes
        toc_float:
            collapsed: false
            smooth_scroll: false
        fig_caption: yes
        theme:
            version: 4
            bootswath: flatly
---

```{r setup, include = FALSE}
library(tidyverse, warn.conflicts = FALSE) # data analysis
library(lubridate, warn.conflicts = FALSE) # work with date time
library(eplusr)                            # integration with EnergyPlus
library(here)                              # project-root-based file path

# disable verbose information
eplusr_option(verbose_info = FALSE)

# install EnergyPlus v9.1 used in this workflow if necessary
if (!is_avail_eplus(9.1)) install_eplus(9.1, local = TRUE)

# load utility functions
source(here("R/utils.R"))
# load functions to calculate statistical indicator
source(here("R/stats.R"))
# load measures to modify the model
source(here("R/measures.R"))
# load functions to read or extract data from simulations
source(here("R/data.R"))
# load fitness functions for optimization
source(here("R/optim.R"))
```

# Workflow

<!-- Create a workflow diagram? -->

- The model we choose with brief description

# Create the initial test model to be calibrated

In order to create a test model for calibration, we modified the values of 6
calibration parameters in the baseline model.

## Read the baseline model

```{r read-init}
# read the baseline model as the starting point for the test model
init <- read_idf(here("data/idf/base.idf"))
```

## Create the initial test model

```{r create-init}
update_material(init, conductivity = 0.8, density = 3800, specific_heat = 600)
update_infiltration(init, infil = 1)
update_people(init, people = 15)
update_lights(init, lpd = 12)
update_equip(init, epd = 10)
update_setpoint(init, core = 26, perimeter = 25)

# save
init$save(here("data/idf/init.idf"), overwrite = TRUE)
```

# Evaluate the performance of the initial init model

## Run initial simulation with IWEC

```{r sim-initial}
# read the initial test model
init <- read_idf(here("data/idf/init.idf"))
# get the file path of IWEC EPW file
path_epw_iwec <- here("data-raw/epw/IWEC/SGP_Singapore.486980_IWEC.epw")

# run annual simulation
init$run(path_epw_iwec, here("data/sim/init"), echo = FALSE)
```

## Extract the simulation results

```{r res-initial}
meter_init <- init %>% extract_electricity()
```

## Visualize the trend

```{r plot-init}
# select one week in July to examine the discrepancy
meter_init %>% weekly_compare(7, 1)
```

## Calculate the statistical indicators

```{r stats-init}
stats_init <- meter_init %>% cal_stats()
```

Current calibration creteria in ASHRAE Guideline 14 for NMBE and CVRMSE is 10%
and 30% respectively.

The initial NMBE and CV(RMSE) is `r stats_init["nmbe"]` and
`r stats_init["cvrmse"]`, respectively.

# Use AMY

```{r run-amy}
# read the initial test model
init <- read_idf(here("data/idf/init.idf"))
# path of AMY EPW
path_epw_amy <- here("data-raw/epw/AMY/SGP_SINGAPORE-CHANGI-AP_486980_18.epw")

# run annual simulation
init$run(path_epw_amy, here("data/sim/amy"), echo = FALSE)
```

```{r stats-amy}
meter_amy <- init %>% extract_electricity()

meter_amy %>% weekly_compare(7, 1)

stats_amy <- meter_amy %>% cal_stats()
```

After using AMY EPW file, the CV(RMSE) is `r stats_amy["cvrmse"]` and `r stats_amy["nmbe"]`.

# Use optimization to calibrate the model

```{r optim}
# define the serach space of each parameter
space_param <- dplyr::tribble(
    ~parameter       , ~lower, ~upper,
     "conductivity"  ,    0.5,   2.0 ,
     "density"       ,   1000,  3000 ,
     "specific_heat" ,    600,  1000 ,
     "infil"         ,      0,    3  ,
     "people"        ,      5,   15  ,
     "lpd"           ,     10,   20  ,
     "epd"           ,     10,   20  ,
     "core"          ,     20,   26  ,
     "perimeter"     ,     20,   26
)

# define setup values
MU <- 2L     # number of individuals per generation
LAMBDA <- 2L # number of generations

# define an ecr control object to store information on the objective function
control <- ecr::initECRControl(calib_fitness, n.objectives = 2, minimize = TRUE)
# initial a logger to store population and fitness
log <- ecr::initLogger(control, log.pop = TRUE)
# initial archive of Pareto front
pareto <- ecr::initParetoArchive(control)

# set evolutionary operators
# use no priors and set all parameters to follow uniform distribution
control <- ecr::registerECROperator(control, "mutate", ecr::mutUniform,
    lower = space_param$lower, upper = space_param$upper)
control <- ecr::registerECROperator(control, "recombine", ecr::recCrossover)
control <- ecr::registerECROperator(control, "selectForMating", ecr::selSimple )
control <- ecr::registerECROperator(control, "selectForSurvival", ecr::selNondom)

# initialize population of MU random values
pop <- ecr::initPopulation(
    MU, ecr::genReal, n.dim = nrow(space_param),
    lower = space_param$lower, upper = space_param$upper)

# evaluate fitness of initial population
fit <- evaluate_fitness(control, pop, 0)

# save fitness in population
for (i in seq_along(pop)) attr(pop[[i]], "fitness") <- fit[, i]

# update log
ecr::updateLogger(log, pop, fit, MU)

# run evolutionary loop
repeat {
    cat(sprintf("Generation [%i]\n", log$env$n.gens))

    # generate offspring
    cat("  * Generate offspring\n")
    offspring <- ecr::generateOffspring(control, pop, fit, LAMBDA, p.recomb = 0.7, p.mut = 0.1)

    cat("  * Evaluate fitness values\n")
    fit_offspring <- evaluate_fitness(control, pop, log$env$n.gens)

    # save fitness in population
    for (i in seq_along(pop)) attr(pop[[i]], "fitness") <- fit[, i]

    cat("  * Prepare next generation\n")
    res <- ecr::replaceMuPlusLambda(control, pop, offspring, fit, fit_offspring)

    pop <- res$population
    fit <- res$fitness

    # do some logging
    cat("  * Update log\n")
    ecr::updateLogger(log, pop, fit, MU)

    cli::cat_line("  * Check whether terminator conditions are met")
    stop_obj <- ecr:::doTerminate(log, list(stopOnMeetCreteria(cvrmse = 0.3, nmbe = 0.1)))

    if (length(stop_obj) > 0L) {
        cat("Terminated:\n")
        cat(sprintf("  < %s: %s >\n", stop_obj$name, stop_obj$message))
        break
    }
}

result <- ecr:::makeECRResult(control, log, pop, fit, stop_obj)
```

# Session Info

```{r session-info}
sessionInfo()
```
